gij bent 2

### 2024-12-09 paper/paper.qmd
Finish discussion of control variables

In general, the control variable results are comparable to the results from [mezelf]. The innovative *gij bent* is more popular in the Brabant dialect area (positive correction), and less popular in the other areas (negative corrections). We even see the same anomaly for the West-Flemish dialect area.[^anomaly] *gij bent* becomes less popular as we move away from northern Antwerp, and more informal tweets also correct towards the conservative *gij zijt* (albeit very slightly, todo). We still see the expected gender effect, where tweets assumed to come from women have a higher probability of the use of *gij bent*. Compared to @sevenants_zijt_2024, some predictors have more subtle effects. Especially the distance correction and the formality distinction correction are smaller. We assume these differences stem from (i) the coefficient attenuation from the elastic net penalty (ii) a difference in dataset size -- @sevenants_zijt_2024 used only one tweet per user because of issues with random effects, which we sidestep by using elastic net regression (iii) parts of the variation attributed to other predictors in  @sevenants_zijt_2024 will now be attributed to individual variation. Still, broadly speaking, the results remain comparable. Therefore, we can safely move on to the discussion of the individual variation.

>>>>

In general, the control variable results are comparable to the results from @sevenants_zijt_2024. The innovative *gij bent* is more popular in the Brabant dialect area (positive correction), and less popular in the other areas (negative corrections). We even see the same anomaly for the West-Flemish dialect area.[^anomaly] *gij bent* becomes less popular as we move away from northern Antwerp, and more informal tweets also correct towards the conservative *gij zijt* (albeit only very slightly). We still see the expected gender effect, where tweets assumed to come from women have a higher probability of the use of *gij bent*. Compared to @sevenants_zijt_2024, some predictors have more subtle effects. Especially the distance correction and the formality distinction correction are smaller. We assume these differences stem from (i) the coefficient attenuation from the elastic net penalty (ii) a difference in dataset size -- @sevenants_zijt_2024 used only one tweet per user because of issues with random effects, which we sidestep by using elastic net regression (iii) parts of the variation attributed to other predictors in @sevenants_zijt_2024 will now be attributed to individual variation. Still, broadly speaking, the results remain comparable. Therefore, we can safely move on to the discussion of the individual variation.
